---
output:
  pdf_document: default
---

```{r, message=FALSE}
library(tidyverse)
library(dplyr)
library(here)
```


```{r, message=FALSE}
# Read in data
snow_survey <- read_csv(here('week1', 'ASDN_Snow_survey.csv'))
```
```{sql connection=}
CREATE TABLE Snow_survey (
    Site TEXT NOT NULL REFERENCES Site(Site),
    Year INTEGER NOT NULL CHECK (Year >= 1900 AND Year <= 2100)),
    Date DATE NOT NULL,
    Plot TEXT NOT NULL,
    Location TEXT NOT NULL,
    Snow_cover REAL NOT NULL CHECK (Snow_cover BETWEEN 0 AND 100),
    Water_cover REAL NOT NULL CHECK (Water_cover BETWEEN 0 AND 100), 
    Land_cover REAL NOT NULL CHECK (Land_cover BETWEEN 0 AND 100),
    Total_cover REAL NOT NULL CHECK (Total_cover = Snow_cover + Water_cover + Land_cover),
    Observer TEXT NOT NULL REFERENCES Personnel(Name),
    Notes TEXT,
    PRIMARY KEY (Site, Year, Date, Plot, Location),
    FOREIGN KEY (Site) REFERENCES Site(Code),
    FOREIGN KEY (Observer) REFERENCES Personnel(Name)
);
```

Process:

Selected appropriate data types based on the nature of the data:
- TEXT for string values (Site, Plot, Location, Observer, and Notes)
- INTEGER for Year, since years are whole numbers
- DATE for the Date column to store date values properly
- REAL for Snow_cover, Water_cover, Land_cover, and Total_cover to store decimal values

Defined a composite primary key consisting of Site, Year, Date, Plot, and Location to uniquely identify each record in the table

Added foreign key constraints referencing the Site(Code) and Personnel(Abbreviation) columns to ensure integrity and create a connection with the Site and Personnel tables

Specified NOT NULL constraints for all columns but Notes to ensure data completeness 

Added CHECK constraints for Snow_cover, Water_cover, and Land_cover to validate that the values fall within the range of 0 to 100 as a percentage

Included a CHECK constraint for Total_cover to make sure the total land cover equals the sum of snow, water, and land covers.

Uncertainties:

Do the Plot and Location columns follow a specific format or pattern? If so this could be accounted for in the table


