---
title: "HW 6"
author: "Maxwell Patterson"
date: "2024-05-24"
---

```{r}
library(dplyr)
library(dbplyr)
library(DBI)
library(duckdb)
library(tidyverse)
```

```{r}
# Connect to the database
conn <- DBI::dbConnect(duckdb::duckdb(), "database.db")

# Load tables 
egg_table <- tbl(conn, "Bird_eggs")
nest_table <- tbl(conn, "Bird_nests")
```

```{r}
# Join the tables and summarize to get total eggs per observer
result <- egg_table %>%
  inner_join(nest_table, by = c("Nest_ID" = "Nest_ID")) %>%
  group_by(Observer) %>%
  summarize(total_eggs = n()) %>%
  arrange(desc(total_eggs)) %>%
  head(3)

# Print output
cat("# Ordered by: desc(total_eggs)\n")
print(collect(result))

# Show the query
show_query(result)
```

Based on the output, dbplyr managed to execute the entire operation in a single SQL query without making a temporary table. The result tell us that dbplyr used SQL LIMIT to limit the output to the first three rows instead of relying on an R tool for limiting the output. This approach shows dbplyr's ability to push down computations to the database engine and perform queries efficiently.
